paper2_resistance_mechanisms_mixtures

### 2016-06-15 inst/documents/paper1_results_figs_rr.Rmd
tidy

```{r}
  #library(devtools)
  #install_github('AndySouth/resistance')
  library(resistance)

@@

<!-- eval=FALSE to stop slow code being executed --> 
```{r, eval=FALSE}

>>>>

```{r,echo=FALSE,results='hide'}
  #library(devtools)
  #install_github('AndySouth/resistance')
  library(resistance)

@@

<!-- eval=FALSE to stop slow code being executed --> 
```{r, eval=FALSE,echo=FALSE,results='hide'}
